Kronos \& Krios: TBD

### 2017-05-04 paper/ms.tex
introduce nicknames

Here, we report and discuss the discovery of a co-moving pair of solar twin stars,
HD~240429 and HD~240430, with unusual chemical abundance and differential abundance patterns
that strongly suggest a dramatic accretion of planetary material by the two stars.
\todo{section summary}

>>>>

Here, we report and discuss the discovery of a co-moving pair of solar twin stars,
HD~240430 and HD~240429, with unusual chemical abundance and differential abundance patterns
that strongly suggest a dramatic accretion of planetary material by the two stars.
We nickname the two stars \bizarreone\ (HD~240430) and
\sunanalog\ (HD~240429) throughout the \documentname.
\todo{section summary}
